### 2020-05-25 myThesis/thesis_LaTeX/main.tex
NFES data collection
thesis  structure

\documentclass[
% The default document font size, options: 10pt, 11pt, 12pt
11pt, 
% Two side (alternating margins) for binding by default, uncomment to switch to one side
%oneside,
% ngerman for German
english,
% Single line spacing, alternatives: onehalfspacing or doublespacing
singlespacing,
% Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%draft,
% If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%nolistspacing,
% Uncomment to add the list of figures/tables/etc to the table of contents
%liststotoc,
% Uncomment to add the main table of contents to the table of contents
%toctotoc,
% Uncomment to add space between paragraphs
%parskip,
% Uncomment to not load the hyperref package
%nohyperref,
% Uncomment to get a line under the header
headsepline,
% Uncomment to place the chapter title next to the number on one line
%chapterinoneline,
% Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
%consistentlayout,
% The class file specifying the document structure
]{MastersDoctoralThesis}

@@

% Output font encoding for international characters
\usepackage[T1]{fontenc}

@@

% Use the bibtex backend with the authoryear citation style (which resembles APA)
\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex}

% The filename of the bibliography
\addbibresource{example.bib}

@@

@@

% Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\thesistitle{Thesis Title}

% Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\supervisor{Dra. Dora \textsc{Medina}}

@@

\vspace*{.06\textheight}
{\scshape\LARGE \univname\par}\vspace{1.5cm} % University name
\textsc{\Large Masters Thesis}\\[0.5cm]      % Thesis type

\HRule \\[0.4cm]                            % Horizontal line
{\huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
\HRule \\[1.5cm]                            % Horizontal line

@@

% Author name - remove the \href bracket to remove the link
%\href{http://www.osamukatagiri.com}{\authorname}
\authorname
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\

% Supervisor name - remove the \href bracket to remove the link
%\href{http://www.doramedina.com}{\supname}
\supname
\end{flushright}
\end{minipage}\\[3cm]

@@

\large \textit{A thesis submitted in fulfillment of the requirements\\ for the degree of
% University requirement text
\degreename}\\[0.3cm]
\textit{in}\\[0.4cm]
% Research group name and department name
\groupname\\\deptname\\[2cm]

@@

@@

%----------------------------------------------------------------------------------------
%	QUOTATION PAGE
%----------------------------------------------------------------------------------------

\vspace*{0.2\textheight}

\noindent\enquote{\itshape Thanks to my solid academic training, today I can write hundreds of words on virtually any topic without possessing a shred of information, which is how I got a good job in journalism.}\bigbreak

\hfill Dave Barry

@@

The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots \\

@@

@@

@@

\begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table

Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
%Constant Name & $Symbol$ & $Constant Value$ with units\\

\end{constants}

@@

$a$ & distance & \si{\meter} \\
$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
%Symbol & Name & Unit \\

@@

%----------------------------------------------------------------------------------------
%	DEDICATION
%----------------------------------------------------------------------------------------

\dedicatory{Dedicated to}
This thesis work is dedicated to my parents, William and Karen Ryan, who have always loved me unconditionally and whose good examples have taught me to work hard for the things that I aspire to achieve. They have been a constant source of support and encouragement during the challenges of graduate school and life. I am truly thankful for having you in my life.

@@

\include{Chapters/Chapter1}
%\include{Chapters/Chapter2} 
%\include{Chapters/Chapter3}
%\include{Chapters/Chapter4} 
%\include{Chapters/Chapter5}

@@

\include{Appendices/AppendixA}
%\include{Appendices/AppendixB}
%\include{Appendices/AppendixC}

\printbibliography[heading=bibintoc]

>>>>

\documentclass[
% The default document font size, options: 10pt, 11pt, 12pt
11pt, 
% Two side (alternating margins) for binding by default, uncomment to switch to one side
oneside,
% ngerman for German
english,
% Single line spacing, alternatives: singlespacing, onehalfspacing or doublespacing
onehalfspacing,
% Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%draft,
% If the document is nolistspacing, onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
onehalfspacing,
% Uncomment to add the list of figures/tables/etc to the table of contents
%liststotoc,
% Uncomment to add the main table of contents to the table of contents
%toctotoc,
% Uncomment to add space between paragraphs
parskip,
% Uncomment to not load the hyperref package
%nohyperref,
% Uncomment to get a line under the header
headsepline,
% Uncomment to place the chapter title next to the number on one line
chapterinoneline,
% Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
consistentlayout,
% The class file specifying the document structure
]{MastersDoctoralThesis}

@@

% Output font encoding for international characters
\usepackage[T1]{fontenc}
\usepackage{textcomp} % support the degree symbol

@@

% Use tu justify paragraphs
\usepackage{ragged2e}

% Use the bibtex backend with the authoryear citation style (which resembles APA)
\usepackage[backend=biber,natbib=true]{biblatex}
% MLA, APA, or IEEE? - https://www.overleaf.com/learn/latex/Biblatex_citation_styles
%\usepackage[style=apa, backend=biber]{biblatex}

% The filename of the bibliography
\addbibresource{mainBiblio.bib}

@@

% to set default colours
\usepackage{xcolor}
\definecolor{mygray}{gray}{0.5}

% for gantt charts
\usepackage{tikz}
\usepackage{gantt}

% to rotate pages in landscape
\usepackage{lscape}

% equation arrows with text
\usepackage{amsmath}

% insert degree celsius symbol
\usepackage{textcomp}

% include other pdf pages
\usepackage{pdfpages}

@@

% Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\thesistitle{Fabrication of graphitic-carbon suspended nanowires through mechanoelectrospinning of photocrosslinkable polymers}

% Your supervisor's name, this is used in the title page, print it elsewhere with \supname and \cosupname
\supervisor{Dr. Héctor Alán \textsc{Aguirre} Soto}
\cosupervisor{Dra. Dora Iliana \textsc{Medina} Medina}

@@

\vspace*{.06\textheight}
{\scshape\LARGE \univname\par} % University name

\begin{center}
\includegraphics[width=0.15\textwidth]{./Figures/uniLogo.png}
\end{center}

\vspace{0.5cm}
\textsc{\Large Masters Thesis Proposal}\\[0.5cm]      % Thesis type

\HRule \\%[0.5cm]                           % Horizontal line
{\huge \bfseries \ttitle\par}\vspace{0.0cm} % Thesis title
\HRule \\[0.5cm]                            % Horizontal line

@@

% Author name - remove the \href bracket to remove the link
\href{https://linkedin.com/in/osamu-katagiri-84b2b940/}{\authorname}
%\authorname
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{flushright} \large
\emph{Principal Advisor:} \\
% Supervisor name - remove the \href bracket to remove the link
%\href{http://www.doramedina.com}{\supname}
\supname

\bigskip

\emph{Co-advisor and\\Director of Program:} \\
% Supervisor name - remove the \href bracket to remove the link
\href{https://www.medinadora.com/}{\cosupname}
%\cosupname
\end{flushright}
\end{minipage}\\[0.5cm]

@@

\large \textit{A thesis proposal submitted in fulfillment of the requirements\\ for the degree of
% University requirement text
\degreename}\\[0.25cm]
\textit{in}\\[0.25cm]
% Research group name and department name
\groupname\\\deptname\\[1cm]

@@

%----------------------------------------------------------------------------------------
%	COMMITTEE'S PAGE
%----------------------------------------------------------------------------------------

%\includepdf[page=-]{./pdf/AlanDoraSigns}

\begin{committee}
\addchaptertocentry{\supervisingcommittee} % Add the the supervising committee to the table of contents
The committee members, hereby, recommend that the proposal by \authorname \text{ }to be accepted to develop the thesis project as a partial requirement for the degree of \degreename.

\begin{flushright} \large

\bigskip
\bigskip
\medskip

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
\supname\\
Tecnológico de Monterrey\\
\emph{Principal Advisor}

\bigskip
\bigskip
\medskip

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
\cosupname\\
Tecnológico de Monterrey\\
\emph{Co-Advisor}

\bigskip
\bigskip
\medskip

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
Dr. Marc \textsc{Madou}\\
Tecnológico de Monterrey\\
\emph{Committee Member}

\bigskip
\bigskip
\medskip

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
Dr. Sergio Omar \textsc{Martínez} Chapa\\
Tecnológico de Monterrey\\
\emph{Committee Member}

\end{flushright}

\begin{center}

\bigskip
\bigskip
\medskip

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
\cosupname \\
\emph{Director of Program in Nanotechnology}\\
School of Engineering and Sciences\\
%\href{http://www.doramedina.com}{\supname}

\bigskip
{\addressname \text{, } \large \today}\\[0cm]

\end{center}
\end{committee}

@@

@@

Carbon nano-wires are versatile materials composed of carbon chains with a wide range of applications due to their high conductivity. Regardless of the high interest in the implementation of carbon nano-wires in several applications and devices, no feasible processes have been developed to fabricate carbon nano-wires with spatial control at a reasonable cost. Carbon nano-wires have been fabricated with the use of a photoresist, but little is known about polymers that can produce more conductive carbon nano-wires after pyrolysis. Various polymer solutions have been tested in near field electrospinning (NFES) and photopolymerization separately, however, few have been tested for nano-wire fabrication purposes through pyrolysis. The intention behind the thesis proposal is to implement rheology analyses of different polymer solutions to determine if they can be easily electrospun at low voltages and then fabricate nano-wires with them. This thesis work arises from the need to test a greater variety of polymers with the goal to design a polymer solution to fabricate carbon nano-wires with better conductivity than the current SU-8 polymeric nano-fibers. The research process will include the design of polymer solutions that can be electrospun, photopolymerized, and then pyrolyzed into conducting carbon nanowires. On the other hand, it is intended to engineer a newly designed polymer solution to achieve mass scale manufacturing of conductive carbon nano-wires in an inexpensive, continuous, simple and reproducible manner as central components for nano-sensors. \\

@@

\textbf{CEM} & \textbf{C}ampus \textbf{E}stado de \textbf{M}éxico\\

\textbf{CNWs} & \textbf{C}arbon \textbf{N}ano-\textbf{w}ire\textbf{s}\\

\textbf{DC} & \textbf{D}irect \textbf{C}urrent\\

\textbf{EMS} & \textbf{E}lectro\textbf{m}echanical \textbf{S}pinning\\

\textbf{FFES} & \textbf{F}ar \textbf{F}ield de \textbf{E}lectro\textbf{s}pinning\\

@@

\textbf{MA} & \textbf{Ma}ssachusetts\\

\textbf{MEMS} & \textbf{M}icro\textbf{e}lectro\textbf{m}echanical \textbf{S}ystems\\

\textbf{MNT} & \textbf{M}aestría en \textbf{N}ano\textbf{t}ecnología \emph{(Master of Science in Nanotechnology)}\\

\textbf{MTY} & \textbf{M}on\textbf{t}erre\textbf{y} \emph{or} Campus \textbf{M}on\textbf{t}erre\textbf{y}\\

\textbf{NFES} & \textbf{N}ear \textbf{F}ield de \textbf{E}lectro\textbf{s}pinning\\

\textbf{USA} & \textbf{U}nited \textbf{S}tates of \textbf{A}merica\\

\textbf{UV} & \textbf{U}ltra\textbf{v}iolet\\

@@

@@

%$a$ & distance & \si{\meter} \\
%$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
Symbol & Name & Unit \\

@@

%\begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table

%Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
%Constant Name & $Symbol$ & $Constant Value$ with units\\

%\end{constants}

@@

\setlength{\parskip}{1.5em} % Paragraph spacing
%\RaggedRight
{\fontsize{12}{15} \selectfont

\include{./Chapters/1}
\include{./Chapters/2}
\include{./Chapters/3}
\include{./Chapters/4}
\include{./Chapters/5}
\include{./Chapters/6}
\include{./Chapters/7}

}

%\include{Chapters/__IntroToLaTeX}

\printbibliography[title={References}]

@@

%\include{Appendices/AppendixA}
%\include{Appendices/AppendixB}
%\include{Appendices/AppendixC}
